Agile Monitoring of Evolving Web Services

### 2018-03-21 restructured.tex
small restructuring

  During binding, the \tool will search for all endpoints defined in the target application. \ins{PERFORMANCE DISCUSSION: this introspection, which looks up endpoints, happens only once at the startup of the service, so it is going to affect the API startup performance, but not the actual endpoint performance. In our case, the overhead here was quite small: TO MEASURE}.

@@

\begin{figure*}[h!]
  \centering
  \subfloat[overview of the tracked endpoints]{\includegraphics[width=0.8\columnwidth]{overview}\label{fig:overview}}
  \subfloat[number of requests per endpoint per day]{\includegraphics[width=.7\columnwidth]{number_of_requests_}\label{fig:aeu}}
  \qquad
  \subfloat[requests per hour heatmap]{\includegraphics[width=0.8\columnwidth]{daily_patterns_}\label{fig:dp}}
  \subfloat[response time (in ms) per monitored endpoint view]{\includegraphics[width=.7\columnwidth]{endpoint_performance_}\label{fig:ep}}\qquad
  \caption{Some of the available views\label{fig:views}}
\end{figure*}

\newpage
\section{How Far Can We Go With One Line of Configuration?}

A discussion must be added here about the types of useful information and problems that can be solved with these views.

  There are three main categories of visual perspectives that are available using \tool:
  \begin{enumerate}
    \item \textit{Service Utilization} presents information about the usage of all endpoints of interest to the developer,
    \item \textit{Endpoint Performance} presents response times of the various service endpoints, and
    \item \textit{User Experience} presents information about the user-perceived performance of monitored service endpoints.
  \end{enumerate}

REQUIREMENT: Adding a time interval is important. 
Otherwise the performance numbers in chart 1 are not good enough... also an outlier very far in the past, will make all the heatmap data points to look very pale in comparison forever after.

\paragraph{Service Utilization}
\label{sec:util}

@@

Figure \ref{fig:aeu} shows a first perspective on endpoint utilization that \tool provides: a stacked bar chart of the number of hits to various endpoints grouped by day\footnote{Endpoint colors are the same in different views}. Figure~\ref{fig:aeu} in particular shows that at its peak the API has about 12.000 hits per day. 
The way users interact with the platform can also be inferred since the endpoints are indicators of different activity types, e.g.:

@@

\paragraph{Endpoint Performance}
\label{sec:perf}

@@

  % \ml{Thijs and Patrick... the visualization people will complain when they see that we have different colors for the same endpoint in different graphs. Can we insure that there is consistency in colors? Simplest trick would be to obtain the color by hashing the name of the endpoint... in that case the same endpoint would have the same color in various graphs.}
  % This is supported in the latest version of the dashboard

%  \begin{figure}[!ht]
%    \centering
%    \includegraphics[width=0.95\linewidth]{endpoint_performance_}
%    \caption{The response time (in ms) per monitored endpoint view allows for identifying performance variability and balancing issues}
%    \label{fig:ep}
%  \end{figure}

@@

      \begin{figure*}[h!]
    \centering
    \includegraphics[width=\linewidth]{outliers}
    \caption{Automatically collected outlier information}
    \label{fig:figure1}
  \end{figure*}

  \section{Automated outlier detection and monitoring}

\begin{figure*}[h!]
  \centering
  \includegraphics[width=0.6\linewidth]{translation_endpoint_evolution_}
  \caption{The Performance Evolution of the \epTranslations endpoint}
  \label{fig:tee}
\end{figure*}

@@

@@

@@

@@

\todo{Summarize the subsections extensively; evaluate which figures to keep and ideally take new screenshots for the ones we keep; consider adding two more views (like Fig. 3.2 of Patrick's thesis)}

% \begin{figure*}[t]
% 	\centering
% 	\subfloat[number of requests per endpoint per day]{\includegraphics[width=.9\columnwidth]{number_of_requests_}\label{fig:aeu}}
% 	\subfloat[requests per hour heatmap]{\includegraphics[width=\columnwidth]{daily_patterns_}\label{fig:dp}}
% 	\qquad
% 	\subfloat[response time (in ms) per monitored endpoint view]{\includegraphics[width=.8\columnwidth]{endpoint_performance_}\label{fig:ep}}\qquad
% 	\subfloat[The Performance Evolution of the \epTranslations endpoint]{\includegraphics[width=.95\columnwidth]{translation_endpoint_evolution_}\label{fig:tee}}
% 	\caption{Some of the available views\label{fig:views}}
% \end{figure*}

>>>>

  During binding, the \tool will search for all endpoints defined in the target application.

@@

In the Zeeguu case study, one of the slowest endpoints, and one with the highest variability as shown in \Fref{fig:ep} is \epFeedItems: it retrieves a list of recommended articles for a given user. However, since a user can be subscribed to anything from one to three dozen article sources, and since the computation of the difficulty is personalized and it is slow, the variability in time among users is likely to be very large.

\begin{figure*}[h!]
  \centering
  \subfloat[number of requests per endpoint per day]{\includegraphics[width=.9\columnwidth]{number_of_requests_}\label{fig:aeu}}
  \subfloat[requests per hour heatmap]{\includegraphics[width=\columnwidth]{daily_patterns_}\label{fig:dp}}
  \caption{Some of the available views\label{fig:views}}
\end{figure*}

\newpage
\section{Service Utilization}
\label{sec:util}

\ins{A discussion must be added here about the types of useful information and problems that can be solved with these views.}

\textit{Service Utilization} presents information about the usage of all endpoints of interest to the developer,

@@

Simplest utilization perspective:

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.5\linewidth]{endpoint-call-count}
  \caption{Caption here}
  \label{fig:figure1}
\end{figure}

% REQUIREMENT: Adding a time interval is important. 
% Otherwise the performance numbers in chart 1 are not good enough... also an outlier very far in the past, will make all the heatmap data points to look very pale in comparison forever after.

Figure \ref{fig:aeu} shows a first perspective on endpoint utilization that \tool provides: a stacked bar chart of the number of hits to various endpoints grouped by day\footnote{Endpoint colors are the same in different views}. Figure~\ref{fig:aeu} in particular shows that at its peak the API has about 12.000 hits per day.

The way users interact with the platform can also be inferred since the endpoints are indicators of different activity types, e.g.:

@@

\newpage
\section{Endpoint Performance}
\label{sec:perf}

@@

 \begin{figure}[!ht]
   \centering
   \includegraphics[width=0.95\linewidth]{endpoint_performance_}
   \caption{The response time (in ms) per monitored endpoint view allows for identifying performance variability and balancing issues}
   \label{fig:ep}
 \end{figure}

@@

\begin{figure}[h!]
  \centering
  \subfloat[overview of the tracked endpoints]{\includegraphics[width=0.8\columnwidth]{overview}\label{fig:overview}}
  \caption{Some of the available views\label{fig:views}}
\end{figure}

@@

  \begin{figure}[h!]
  \centering
  \includegraphics[width=0.8\linewidth]{translation_endpoint_evolution_}
  \caption{The Performance Evolution of the \epTranslations endpoint}
  \label{fig:tee}
\end{figure}

@@

  \begin{figure*}[h!]
    \centering
    \includegraphics[width=\linewidth]{outliers}
    \caption{Automatically collected outlier information}
    \label{fig:figure1}
  \end{figure*}
  \newpage
  \section{Automated outlier detection and monitoring}

@@

\ins{PERFORMANCE DISCUSSION: this introspection, which looks up endpoints, happens only once at the startup of the service, so it is going to affect the API startup performance, but not the actual endpoint performance. In our case, the overhead here was quite small: TO MEASURE}.

@@

\todo{evaluate which figures to keep and ideally take new screenshots for the ones we keep; consider adding two more views (like Fig. 3.2 of Patrick's thesis)}
